---
title: "CMP_Suisun_nutrients_script"
author: "Denise Colombano"
date: "November 29, 2018"
output: html_document
---

# Libraries
```{r}
library(tidyverse)
library(lubridate)
```

** For final tidy dataframe, skip down to Step 3**

Notes:

- Raw data originates from three different spreadsheets: (1) Dahlgren lab values of EC, 
pH, turbidity, TSS, VSS, measured by undergraduate interns; (2) Dahlgren lab values of
nutrients such as nitrate, phosphate, etc., measured by the lab manager Xien; (3) field
data records of when the autosampler samples were taken in the field. All of the field
record timestamps (hourly) were rounded to the nearest 15-min interval to match up to the 
sonde data recorded nearby and have the extension "DLS" to match up with the Daylight 
Savings corrected date-times in the sonde files.

- In step 1 below, I export my nutrient dataset for each site and then use that csv to
manually add columns in Excel for "Deployment" and "Time". It should be the only time that
I go back and forth between Excel and R. (It's not worth coding it). The autosampler start
times can be found on the Box website (https://ucdavis.app.box.com/folder/46200246118)

- As of 11/29/2018, we should get the Chl-a lab values soon and we can add them to this
dataset and then use them to calibrate the field values measured by the sonde.

- The number of types of nutrients measured are different for 2017 and 2018. There may
need to be some conversions of units (all of which are specified in column names)


Step 1.

Import QC'd data from grab samples in 2017. The raw datasheets include all sites, but I 
will separate them by site for tidying.


# Import nutrient data

## 2017
```{r}
nutrients17 <- read_csv("nutrients/Data/CMP_Data_Nutrients_All_SummerFall_2017.csv")
View(nutrients17)

# lubridate
nutrients17$Date <- mdy(nutrients17$Date)
nutrients17$ID2 <- 1:899
```

### First Mallard
```{r}
# subset FM
fmnut17 <- nutrients17 %>% 
  filter(Site=="FM" | Site=="F M") %>%  # someone entered a space by accident
  mutate(Site="FM") # remove the space

#fmnut17 %>% write_csv("nutrients/Data_output/CMP_Data_FirstMallard_Nutrients_SummerFall_2017.csv")

# In Excel, find autosampler start times from field data sheet, add to this csv
# reimport updated file with the "_Auto" name

fmnut17_auto <- 
  read_csv("nutrients/Data_output/CMP_Data_FirstMallard_Nutrients_SummerFall_2017_Auto.csv") %>% 
  rename(ID=CMP)
View(fmnut17_auto)

# lubridate
fmnut17_auto$Date <- mdy(fmnut17_auto$Date)

# unite Date and Time and round to nearest 15 min interval in new datetime column
fmnut17_auto <- fmnut17_auto %>% 
  unite("datetime", c("Date","Time"), sep=" ")

#lubridate
fmnut17_auto$datetime <- as_datetime(fmnut17_auto$datetime) 
fmnut17_auto$datetime_DLS <- round_date(fmnut17_auto$datetime, "15 mins") # match sondes

head(fmnut17_auto) # et voila!

# export df
#fmnut17_auto %>% 
 # write_csv("nutrients/Data_output/CMP_Data_FirstMallard_Nutrients_2017_Tidied.csv")
```

### Sheldrake
```{r}
# subset SD
sdnut17 <- nutrients17 %>% 
  filter(Site=="SD" | Site=="S D") %>%  # someone entered a space by accident
  mutate(Site="SD") # remove the space

#sdnut17 %>% write_csv("nutrients/Data_output/CMP_Data_Sheldrake_Nutrients_SummerFall_2017.csv")

# In Excel, find autosampler start times from field data sheet, add to this csv
# reimport updated file with the "_Auto" name

sdnut17_auto <- 
  read_csv("nutrients/Data_output/CMP_Data_Sheldrake_Nutrients_SummerFall_2017_Auto.csv")
View(sdnut17_auto)

# lubridate
sdnut17_auto$Date <- mdy(sdnut17_auto$Date, tz="America/Los_Angeles")

# unite Date and Time and round to nearest 15 min interval in new datetime column
sdnut17_auto <- sdnut17_auto %>% 
  unite("datetime", c("Date","Time"), sep=" ")

#lubridate
sdnut17_auto$datetime <- as_datetime(sdnut17_auto$datetime, tz="America/Los_Angeles") 
sdnut17_auto$datetime_DLS <- round_date(sdnut17_auto$datetime, "15 mins")

head(sdnut17_auto) # et voila!

# export df
#sdnut17_auto %>% 
 # write_csv("nutrients/Data_output/CMP_Data_Sheldrake_Nutrients_2017_Tidied.csv")
```

### Peytonia
```{r}
# subset PT
ptnut17 <- nutrients17 %>% 
  filter(Site=="PT")

ptnut17 %>% write_csv("nutrients/Data_output/CMP_Data_Peytonia_Nutrients_SummerFall_2017.csv")

# In Excel, find autosampler start times from field data sheet, add to this csv
# reimport updated file with the "_Auto" name

ptnut17_auto <- 
  read_csv("nutrients/Data_output/CMP_Data_Peytonia_Nutrients_SummerFall_2017_Auto.csv")
View(ptnut17_auto)

# lubridate
ptnut17_auto$Date <- mdy(ptnut17_auto$Date, tz="America/Los_Angeles")

# unite Date and Time and round to nearest 15 min interval in new datetime column
ptnut17_auto <- ptnut17_auto %>% 
  unite("datetime", c("Date","Time"), sep=" ")

#lubridate
ptnut17_auto$datetime <- as_datetime(ptnut17_auto$datetime, tz="America/Los_Angeles") 
ptnut17_auto$datetime_DLS <- round_date(ptnut17_auto$datetime, "15 mins")

head(ptnut17_auto) # et voila!

# export df
#ptnut17_auto %>% 
 # write_csv("nutrients/Data_output/CMP_Data_Peytonia_Nutrients_2017_Tidied.csv")

# note: PT bottle #0 was a single water grab
```

### Hill Slough
```{r}
# subset HL
hlnut17 <- nutrients17 %>% 
  filter(Site=="HL" | Site=="H L") %>%  # someone entered a space by accident
  mutate(Site="HL") # fix space
  
hlnut17 %>% write_csv("nutrients/Data_output/CMP_Data_Hill_Nutrients_SummerFall_2017.csv")

hlnut17_id2 <- hlnut17 %>% # query these columns to join back to dataset later
  select(ID, ID2) # I forgot to include it in my Excel sheet; lazy workaround

# In Excel, find autosampler start times from field data sheet, add to this csv
# reimport updated file with the "_Auto" name

hlnut17_auto <- 
  read_csv("nutrients/Data_output/CMP_Data_Hill_Nutrients_SummerFall_2017_Auto.csv") %>% 
  filter(!is.na(Bottle)) %>%  # remove grab samples collected on first day, no timestamp (n=3)
  inner_join(hlnut17_id2, by="ID") # join back ID2 column
View(hlnut17_auto)

# lubridate
hlnut17_auto$Date <- mdy(hlnut17_auto$Date, tz="America/Los_Angeles")

# unite Date and Time and round to nearest 15 min interval in new datetime column
hlnut17_auto <- hlnut17_auto %>% 
  unite("datetime", c("Date","Time"), sep=" ")

#lubridate
hlnut17_auto$datetime <- as_datetime(hlnut17_auto$datetime, tz="America/Los_Angeles") 
hlnut17_auto$datetime_DLS <- round_date(hlnut17_auto$datetime, "15 mins")

head(hlnut17_auto) # et voila!

# export df
#hlnut17_auto %>% 
 # write_csv("nutrients/Data_output/CMP_Data_Hill_Nutrients_2017_Tidied.csv")

# note: HL bottle #0 was a single water grab
```

### All sites
```{r}
nutall17 <- rbind(fmnut17_auto, sdnut17_auto, ptnut17_auto, hlnut17_auto) %>% 
  mutate(Yr="2017")

nutall17 %>% write_csv("nutrients/Data_output/CMP_Data_Nutrients_All_Sites_2017_Tidied.csv")
```



Step 2.

Import QC'd data from grab samples in 2018. The autosampler start times were manually
entered in the QC'd dataset beforehand; don't need an extra step of exporting/ importing.

- First import data recorded by undergrad interns (EC, pH, Turb, TSS, VSS)
- Second import Xien's nutrient data (DOC, TN, TP, etc)

- Note: It looks like the units measured are different than in 2017. Also, we decided
to measure a subset of nutrients compared to the first year, so there will be less columns.
I believe you need to use the grams of water filtered to calculate the TSS/ VSS mg/L to get
the same units as 2017. (TSS is measured after being combusted in the 60C oven; VSS is 510C)

## 2018
```{r}
# part 1
nut18_p1 <- read_csv("nutrients/Data/CMP_Nutrients_2018_QAQC_112918.csv") # lab WQ values
nut18_p2 <- read_csv("nutrients/Data/CMP_Nutrients_2018_QAQC_112918_part2.csv") # Xien nutrients

# POSIXct format
nut18_p1$Date <- mdy(nut18_p1$Date)
nut18_p2$Date <- mdy(nut18_p2$Date)
```

### All sites
```{r}
# this join creates a df with only QC'd data, with 1145 rows, removes data in pt 2 
# that got thrown out when we recollected the samples from May 2018 at 2 sites
nutall18 <- nut18_p1 %>% 
  left_join(nut18_p2, by=c("Bottle", "Date", "Site", "ID"))

# unite Date and Time and round to nearest 15 min interval in new datetime column
nutall18 <- nutall18 %>% 
  unite("datetime", c("Date","Time"), sep=" ")

#lubridate
nutall18$datetime <- as_datetime(nutall18$datetime, tz="America/Los_Angeles") 
nutall18$datetime_DLS <- round_date(nutall18$datetime, "15 mins")
nutall18$Yr <- year(nutall18$datetime)

# export df
#nutall18 %>% write_csv("nutrients/Data_output/CMP_Data_Nutrients_All_Sites_2018_Tidied.csv")
```

Step 3. 

These are the final tidy dataframes you can use for data analysis and match up to sonde
data using the "datetime_DLS" column.

# Reimport tidy data
```{r}
nut17_tidied <- read_csv("nutrients/Data_output/CMP_Data_Nutrients_All_Sites_2017_Tidied.csv")
View(nut17_tidied)

nut18_tidied <- read_csv("nutrients/Data_output/CMP_Data_Nutrients_All_Sites_2018_Tidied.csv")
View(nut18_tidied)
```

