---
title: "CMP_Suisun_sondes_script"
author: "Denise Colombano"
date: "November 28, 2018"
output: html_document
---

# Libraries
```{r}
library(tidyverse)
library(lubridate)
```

**For final tidy dataframe, skip down to Step 5**

Units of measurement:

Temp: water temperature measured in degrees Celsius (C)																							
SpCond: specific conductivity measured in milli-Siemens per centimeter (mS/cm)
CondmS/cm: conductivity measured in milli-Siemens per centimeter (mS/cm)
Sal: salinity measured in parts per thousand (psu)																							
DO_pct: dissolved oxygen measured in percent saturation (%)		
DO_mgl: dissolved oxygen concentration measured in milligrams per Liter (mg/L)									
Depth: sonde depth measured in meters (m)
Turb: turbidity measured in either formazin nephelometric or nephelometric turbidity units (FNU/NTU) based on sensor; considered to be equivalent for SWMP purposes.


Notes:

- This script is the first exercise and accompanies the "CMP_Suisun_nutrients_script2"

- I manually removed rows in the original files where the sonde was on and
recording data but out of the water (i.e., being transported to/ from the site)

- I discovered that the desired parameter, Specific conductivity (mS/cm), was not
measured from July to September 2017. I created NA placeholders for these values
in instances when this occurred. I recommend using salinity (ppt) and temperature (C)
to retroactively calculate Specific conductivity (mS/cm) to fill in NAs.

- The NERR records 15-min continuous data using standard local time (in winter). Because 
the study was conducted during months in the Daylight Savings period (spring and summer),
I created an additional column called "datetime_DLS" which is corrected for Daylight
Savings.

- The chlorophyll measurements have not yet been calibrated by water grabs; the
Dahlgren lab is still conducting lab analyses on these filtered samples. Once we 
receive them, they'll be used to create a "Chlorophyll_corrected" column.

- If the user wants to use R projects to recreate my file path configuration, make 
the following folder structure (which I will specify in a zip file format). The 
folder "Data" has raw data; the folder "Data_output" has tidy data.

CMP_hydro
  sondes
    Data
      FirstMallard
      LowerHill
      LowerPeytonia
      Sheldrake
    Data_output
  nutrients
    Data
    Data_output

- I used hashtags to render "write_csv" functions inactive; you have to remove the
hashtag and run the function if you want to write over my filename with a new one.
This is to prevent the user from writing over/ changing the file that is in the
Data_output folder I provide, unless desired of course. I recommend changing the 
file name to avoid confusion if you do do this. Also: "write_csv" uses the package
"readr" and it is non-trivial choice when exporting datetime POSIXct data, 
beware of changing it to the "write.csv" base function

--

Step 1. 

Import QC'd wq data generated from the SFSU NERR lab (subcontractors), which is compliant 
with the SWMP long-term monitoring station standards.

# Import wq data

## Sheldrake
```{r}
# IMPORT DATA
# 2017
sd_june17 <- read_csv("sondes/Data/Sheldrake/sfbsdwq060817_QC.csv") %>% # checked
  mutate(Deployment="2017-06-08")

sd_july17 <- read_csv("sondes/Data/Sheldrake/sfbsdwq070617_QC.csv") %>% # checked
  mutate(Deployment="2017-07-06")

sd_july17_2 <- read_csv("sondes/Data/Sheldrake/sfbsdwq072017_QC.csv") %>% # checked
  mutate(Deployment="2017-07-20")

sd_aug17 <- read_csv("sondes/Data/Sheldrake/sfbsdwq081817_QC.csv") %>% # checked
  mutate(Deployment="2017-08-18")

sd_sep17 <- read_csv("sondes/Data/Sheldrake/sfbsdwq091417_QC.csv") %>% 
  mutate(Deployment="2017-09-14") # removed negative depth rows at end in Excel

# 2018
sd_apr18 <- read_csv("sondes/Data/Sheldrake/SS041318_QC.csv") %>% 
  mutate(Deployment="2018-04-13") # removed first 15 rows in Excel and last row to clean up points taken before/after sonde deployment

sd_may18 <- read_csv("sondes/Data/Sheldrake/SS051118_QC.csv") %>% 
  mutate(Deployment="2018-05-11") # removed last row in Excel

sd_jun18 <- read_csv("sondes/Data/Sheldrake/SS060718_QC.csv") %>% 
  mutate(Deployment="2018-06-07") # removed last row in Excel

sd_jul18 <- read_csv("sondes/Data/Sheldrake/SS070518_QC.csv") %>% 
  mutate(Deployment="2018-07-05") # removed last row in Excel

sd_aug18 <- read_csv("sondes/Data/Sheldrake/sfbwqss080218_QC.csv") %>% 
  mutate(Deployment="2018-08-02") # removed last row in Excel

sd_sep18 <- read_csv("sondes/Data/Sheldrake/sfbwqss083018_QC.csv") %>% 
  mutate(Deployment="2018-08-30") # removed first row and last 5


# SUBSET DATA
## Note: from July to September 2017, Sp Cond uS/cm was not measured by accident.
## Need to use salinity (ppt) and temperature (*C) to calculate Sp Cond. Here I
## put a temporary placeholder NA value for that future calculation.

# 2017
sd1wq <- sd_june17 %>% 
  select(Date, Time, SiteName, Depth, Turb, DO_mgl, DO_pct, Temp, Sal, `CondmS/cm`, SpCond,
         pH, ChlorophyllugL, fDOMQSU, Deployment)

sd2wq <- sd_july17 %>% 
  select(Date, Time, SiteName, Depth, Turb, DO_mgl, DO_pct, Temp, Sal, SpCond,
         pH, ChlorophyllugL, fDOMQSU, Deployment) %>%
  mutate(`CondmS/cm`=NA) # placeholder: no CondmS/cm measured

sd3wq <- sd_july17_2 %>% 
  select(Date, Time, SiteName, Depth, Turb, DO_mgl, DO_pct, Temp, Sal, SpCond,
         pH, ChlorophyllugL, fDOMQSU, Deployment) %>%
  mutate(`CondmS/cm`=NA) # # placeholder: no CondmS/cm measured
  
sd4wq <- sd_aug17 %>% 
  select(Date, Time, SiteName, Depth, Turb, DO_mgl, DO_pct, Temp, Sal, SpCond,
         pH, ChlorophyllugL, fDOMQSU, Deployment) %>%
  mutate(`CondmS/cm`=NA) # placeholder: no CondmS/cm measured

sd5wq <- sd_sep17 %>% 
  select(Date, Time, SiteName, Depth, Turb, DO_mgl, DO_pct, Temp, Sal, SpCond,
         pH, ChlorophyllugL, fDOMQSU, Deployment) %>% 
  mutate(`CondmS/cm`=NA) # placeholder: no CondmS/cm measured

# bind subset df together
sd_wq_bind17 <-  rbind(sd1wq,sd2wq,sd3wq,sd4wq,sd5wq)

# create datetime column and specify as POSIXct format
sd_wq_bind17 <- sd_wq_bind17 %>%  
  unite(datetime,Date,Time, sep=" ") 
sd_wq_bind17$datetime <- mdy_hms(sd_wq_bind17$datetime)


# 2018
sd6wq <- sd_apr18 %>% 
  select(Date, Time, SiteName, Depth, Turb, DO_mgl, DO_pct, Temp, `CondmS/cm`, Sal, SpCond,
         pH, ChlorophyllugL, fDOMQSU, Deployment)

sd7wq <- sd_may18 %>% 
  select(Date, Time, SiteName, Depth, Turb, DO_mgl, DO_pct, Temp, `CondmS/cm`, Sal, SpCond,
         pH, ChlorophyllugL, fDOMQSU, Deployment)

sd8wq <- sd_jun18 %>% 
  select(Date, Time, SiteName, Depth, Turb, DO_mgl, DO_pct, Temp, `CondmS/cm`, Sal, SpCond,
         pH, ChlorophyllugL, fDOMQSU, Deployment)

sd9wq <- sd_jul18 %>% 
  select(Date, Time, SiteName, Depth, Turb, DO_mgl, DO_pct, Temp, `CondmS/cm`, Sal, SpCond,
         pH, ChlorophyllugL, fDOMQSU, Deployment)

sd10wq <- sd_aug18 %>% 
  select(Date, Time, SiteName, Depth, Turb, DO_mgl, DO_pct, Temp, `CondmS/cm`, Sal, SpCond,
         pH, ChlorophyllugL, fDOMQSU, Deployment) 

sd11wq <- sd_sep18 %>% 
  mutate(`CondmS/cm`=ConduScm/1000) %>% # convert to mS/cm
  select(Date, Time, SiteName, Depth, Turb, DO_mgl, DO_pct, Temp, `CondmS/cm`, Sal, SpCond,
         pH, ChlorophyllugL, fDOMQSU, Deployment)

# bind subset df together
sd_wq_bind18 <- rbind(sd6wq, sd7wq, sd8wq, sd9wq, sd10wq, sd11wq)

# create datetime column and specify as POSIXct format
sd_wq_bind18 <- sd_wq_bind18 %>%  
  unite(datetime,Date,Time, sep=" ") 
sd_wq_bind18$datetime <- mdy_hms(sd_wq_bind18$datetime)

# BIND THEM TOGETHER AND CORRECT FOR DAYLIGHT SAVINGs
sd_wq_bindall <- rbind(sd_wq_bind17, sd_wq_bind18)

sd_wq_bindall$datetime <- ymd_hms(sd_wq_bindall$datetime, tz="America/Los_Angeles")
sd_wq_bindall$Deployment <- as_date(sd_wq_bindall$Deployment)

# final tidied df
sd_wq_bindall2 <- sd_wq_bindall %>% 
  mutate(datetime_DLS= datetime + hours(1)) %>%  # adjust for DLS
  mutate(SiteName="SD") %>% # SD= sheldrake
  # now round digits to match the NERR dataframe
  mutate(Depth=round(Depth, digits=2), Turb=round(Turb, digits=0), 
         DO_mgl=round(DO_mgl, digits=1), DO_pct=round(DO_pct, digits=1),
         Temp=round(Temp, digits=1), `CondmS/cm`=round(`CondmS/cm`, digits=2),
         SpCond=round(SpCond, digits=2), Sal=round(Sal, digits=1), pH=round(pH, digits=1))

# export df - 11/29/2018
# only execute this if you intend to write over file in folder
#sd_wq_bindall2 %>% 
 # write_csv("sondes/Data_output/CMP_Data_Sheldrake_Sonde_2017_2018_Tidied.csv")
```


## Lower Peytonia
```{r}
# IMPORT DATA
# 2017
pt_june17 <- read_csv("sondes/Data/LowerPeytonia/sfblpwq060517_QC.csv") %>% 
  mutate(Deployment="2017-06-08") # removed first 294 rows in Excel

pt_july17 <- read_csv("sondes/Data/LowerPeytonia/sfblpwq070617_QC.csv") %>% 
  mutate(Deployment="2017-07-06") # checked

pt_july17_2 <- read_csv("sondes/Data/LowerPeytonia/sfblpwq072017_QC.csv") %>% 
  mutate(Deployment="2017-07-20") # checked

pt_aug17 <- read_csv("sondes/Data/LowerPeytonia/sfblpwq081817_QC.csv") %>% 
  mutate(Deployment="2017-08-18") # checked

pt_sep17 <- read_csv("sondes/Data/LowerPeytonia/sfblpwq091417_QC.csv") %>% 
  mutate(Deployment="2017-09-14") # checked

# 2018
pt_apr18 <- read_csv("sondes/Data/LowerPeytonia/LP041318_QC.csv") %>% 
  mutate(Deployment="2018-04-13") # checked

pt_may18 <- read_csv("sondes/Data/LowerPeytonia/LP051118_QC.csv") %>% 
  mutate(Deployment="2018-05-11") # checked

pt_jun18 <- read_csv("sondes/Data/LowerPeytonia/LP060718_QC.csv") %>% 
  mutate(Deployment="2018-06-07") # removed last row

pt_jul18 <- read_csv("sondes/Data/LowerPeytonia/LP070518_QC.csv") %>% 
  mutate(Deployment="2018-07-05") # removed a bunch at the end

pt_aug18 <- read_csv("sondes/Data/LowerPeytonia/sfbwqlp080218_QC.csv") %>% 
  mutate(Deployment="2018-08-02") # removed first two rows and last 302 rows

pt_sep18 <- read_csv("sondes/Data/LowerPeytonia/sfbwqlp083018_QC.csv") %>% 
  mutate(Deployment="2018-08-30") # removed last 5 rows


# SUBSET DATA
# 2017
pt1wq <- pt_june17 %>% 
  select(Date, Time, SiteName, Depth, Turb, DO_mgl, DO_pct, Temp, `CondmS/cm`, Sal, SpCond,
         pH, ChlorophyllugL, fDOMQSU, Deployment)

pt2wq <- pt_july17 %>% 
  select(Date, Time, SiteName, Depth, Turb, DO_mgl, DO_pct, Temp, Sal, SpCond,
         pH, ChlorophyllugL, fDOMQSU, Deployment) %>%
  mutate(`CondmS/cm`=NA) # placeholder: no CondmS/cm measured

pt3wq <- pt_july17_2 %>%
  select(Date, Time, SiteName, Depth, Turb, DO_mgl, DO_pct, Temp, Sal, SpCond,
         pH, ChlorophyllugL, fDOMQSU, Deployment) %>%
  mutate(`CondmS/cm`=NA) # placeholder: no CondmS/cm measured

pt4wq <- pt_aug17 %>%
  select(Date, Time, SiteName, Depth, Turb, DO_mgl, DO_pct, Temp, Sal, SpCond,
         pH, ChlorophyllugL, fDOMQSU, Deployment) %>%
  mutate(`CondmS/cm`=NA) # placeholder: no CondmS/cm measured

pt5wq <- pt_sep17 %>%
  select(Date, Time, SiteName, Depth, Turb, DO_mgl, DO_pct, Temp, Sal, SpCond,
         pH, ChlorophyllugL, fDOMQSU, Deployment) %>%
  mutate(`CondmS/cm`=NA) # placeholder: no CondmS/cm measured

# 2018
pt6wq <- pt_apr18 %>% 
  select(Date, Time, SiteName, Depth, Turb, DO_mgl, DO_pct, Temp, `CondmS/cm`, Sal, SpCond,
         pH, ChlorophyllugL, fDOMQSU, Deployment)

pt7wq <- pt_may18 %>%
  select(Date, Time, SiteName, Depth, Turb, DO_mgl, DO_pct, Temp, `CondmS/cm`, Sal, SpCond,
         pH, ChlorophyllugL, fDOMQSU, Deployment)

pt8wq <- pt_jun18 %>%
  select(Date, Time, SiteName, Depth, Turb, DO_mgl, DO_pct, Temp, `CondmS/cm`, Sal, SpCond,
         pH, ChlorophyllugL, fDOMQSU, Deployment)

pt9wq <- pt_jul18 %>%
  select(Date, Time, SiteName, Depth, Turb, DO_mgl, DO_pct, Temp, `CondmS/cm`, Sal, SpCond,
         pH, ChlorophyllugL, fDOMQSU, Deployment)

pt10wq <- pt_aug18 %>%
  select(Date, Time, SiteName, Depth, Turb, DO_mgl, DO_pct, Temp, `CondmS/cm`, Sal, SpCond,
         pH, ChlorophyllugL, fDOMQSU, Deployment)

pt11wq <- pt_sep18 %>%
  mutate(`CondmS/cm`=ConduScm/1000) %>% # convert to mS/cm
  select(Date, Time, SiteName, Depth, Turb, DO_mgl, DO_pct, Temp, `CondmS/cm`, Sal, SpCond,
         pH, ChlorophyllugL, fDOMQSU, Deployment)

# bind subset df together
pt_wq_bind <- rbind(pt1wq,pt2wq,pt3wq,pt4wq,pt5wq, pt6wq, pt7wq, pt8wq, pt9wq, pt10wq, pt11wq)

# create datetime column and specify as POSIXct format
pt_wq_bind2 <- pt_wq_bind %>%  
  unite(datetime,Date,Time, sep=" ") 
pt_wq_bind2$datetime <- mdy_hms(pt_wq_bind2$datetime, tz="America/Los_Angeles")
pt_wq_bind2$Deployment <- as_date(pt_wq_bind2$Deployment)

# final tidied df
pt_wq_bind3 <- pt_wq_bind2 %>% 
  mutate(datetime_DLS= datetime + hours(1)) %>%  # adjust for DLS
  mutate(SiteName="PT") %>% # PT = peytonia
  # now round digits to match the NERR dataframe
  mutate(Depth=round(Depth, digits=2), Turb=round(Turb, digits=0), 
         DO_mgl=round(DO_mgl, digits=1), DO_pct=round(DO_pct, digits=1),
         Temp=round(Temp, digits=1), `CondmS/cm`=round(`CondmS/cm`, digits=2),
         SpCond=round(SpCond, digits=2), Sal=round(Sal, digits=1), pH=round(pH, digits=1))

# export df- 11/29/2018
#pt_wq_bind3 %>% 
 # write_csv("sondes/Data_output/CMP_Data_Peytonia_Sonde_2017_2018_Tidied.csv")
```

## Lower Hill
```{r}
# IMPORT DATA
# 2017
hl_june17 <- read_csv("sondes/Data/LowerHill/sfblhwq060517_QC.csv") %>% 
  mutate(Deployment="2017-06-08") # remove first 288 rows from Excel file

hl_july17 <- read_csv("sondes/Data/LowerHill/sfblhwq070617_QC.csv") %>% 
  mutate(Deployment="2017-07-06") # QC

hl_july17_2 <- read_csv("sondes/Data/LowerHill/sfblhwq072017_QC.csv") %>% 
  mutate(Deployment="2017-07-20") # QC

hl_aug17 <- read_csv("sondes/Data/LowerHill/sfblhwq081817_QC.csv") %>% 
  mutate(Deployment="2017-08-18") # QC

hl_sep17 <- read_csv("sondes/Data/LowerHill/sfblhwq091417_QC.csv") %>% 
  mutate(Deployment="2017-09-14") # QC

# 2018
hl_apr18 <- read_csv("sondes/Data/LowerHill/LHS041318_QC.csv") %>% 
  mutate(Deployment="2018-04-13") # Removed first 14 rows and last row

hl_may18 <- read_csv("sondes/Data/LowerHill/LHS051118_QC.csv") %>% 
  mutate(Deployment="2018-05-11") # Removed last 2 rows

hl_jun18 <- read_csv("sondes/Data/LowerHill/LHS060718_QC.csv") %>% 
  mutate(Deployment="2018-06-07") # Removed last row

hl_jul18 <- read_csv("sondes/Data/LowerHill/LHS070518_QC.csv") %>% 
  mutate(Deployment="2018-07-05") # Removed last row

hl_aug18 <- read_csv("sondes/Data/LowerHill/sfbwqlhs080218_QC.csv") %>% 
  mutate(Deployment="2018-08-02") # QC

hl_sep18 <- read_csv("sondes/Data/LowerHill/sfbwqlhs083018_QC.csv") %>% 
  mutate(Deployment="2018-08-30") # Removed last 4 rows

# SUBSET
# 2017
hl1wq <- hl_june17 %>%
  select(Date, Time, SiteName, Depth, Turb, DO_mgl, DO_pct, Temp, `CondmS/cm`, SpCond, Sal, 
         pH, ChlorophyllugL, fDOMQSU, Deployment)

hl2wq <- hl_july17 %>%
  select(Date, Time, SiteName, Depth, Turb, DO_mgl, DO_pct, Temp, Sal, SpCond,
         pH, ChlorophyllugL, fDOMQSU, Deployment) %>%
  mutate(`CondmS/cm`=NA) # placeholder: no CondmS/cm measured

hl3wq <- hl_july17_2 %>%
  select(Date, Time, SiteName, Depth, Turb, DO_mgl, DO_pct, Temp, Sal, SpCond,
         pH, ChlorophyllugL, fDOMQSU, Deployment) %>%
  mutate(`CondmS/cm`=NA) # placeholder: no CondmS/cm measured

hl4wq <- hl_aug17 %>%
  select(Date, Time, SiteName, Depth, Turb, DO_mgl, DO_pct, Temp, Sal, SpCond,
         pH, ChlorophyllugL, fDOMQSU, Deployment) %>%
  mutate(`CondmS/cm`=NA) # placeholder: no CondmS/cm measured

hl5wq <- hl_sep17 %>%
  select(Date, Time, SiteName, Depth, Turb, DO_mgl, DO_pct, Temp, Sal, SpCond,
         pH, ChlorophyllugL, fDOMQSU, Deployment) %>%
  mutate(`CondmS/cm`=NA) # placeholder: no CondmS/cm measured

# 2018
hl6wq <- hl_apr18 %>%
  select(Date, Time, SiteName, Depth, Turb, DO_mgl, DO_pct, Temp, `CondmS/cm`, Sal, SpCond,
         pH, ChlorophyllugL, fDOMQSU, Deployment)

hl7wq <- hl_may18 %>%
  select(Date, Time, SiteName, Depth, Turb, DO_mgl, DO_pct, Temp, `CondmS/cm`, Sal, SpCond,
         pH, ChlorophyllugL, fDOMQSU, Deployment)

hl8wq <- hl_jun18 %>%
  select(Date, Time, SiteName, Depth, Turb, DO_mgl, DO_pct, Temp, `CondmS/cm`, Sal, SpCond,
         pH, ChlorophyllugL, fDOMQSU, Deployment)

hl9wq <- hl_jul18 %>%
  select(Date, Time, SiteName, Depth, Turb, DO_mgl, DO_pct, Temp, `CondmS/cm`, Sal, SpCond,
         pH, ChlorophyllugL, fDOMQSU, Deployment)

hl10wq <- hl_aug18 %>%
  select(Date, Time, SiteName, Depth, Turb, DO_mgl, DO_pct, Temp, `CondmS/cm`, Sal, SpCond,
         pH, ChlorophyllugL, fDOMQSU, Deployment)

hl11wq <- hl_sep18 %>%
  mutate(`CondmS/cm`=ConduScm/1000) %>% # convert to mS/cm
  select(Date, Time, SiteName, Depth, Turb, DO_mgl, DO_pct, Temp, `CondmS/cm`, Sal, SpCond,
         pH, ChlorophyllugL, fDOMQSU, Deployment)

# bind subset df together
hl_wq_bind <- rbind(hl1wq,hl2wq,hl3wq,hl4wq,hl5wq, hl6wq, hl7wq, hl8wq, hl9wq, hl10wq, hl11wq)

# create datetime column and specify as POSIXct format
hl_wq_bind2 <- hl_wq_bind %>%
  unite(datetime,Date,Time, sep=" ")
hl_wq_bind2$datetime <- mdy_hms(hl_wq_bind2$datetime, tz="America/Los_Angeles")
hl_wq_bind2$Deployment <- as_date(hl_wq_bind2$Deployment)

# final tidied df
hl_wq_bind3 <- hl_wq_bind2 %>% 
  mutate(datetime_DLS= datetime + hours(1)) %>%  # adjust for DLS
  mutate(SiteName="HL") %>% # HL = Hill
  # now round digits to match the NERR dataframe
  mutate(Depth=round(Depth, digits=2), Turb=round(Turb, digits=0), 
         DO_mgl=round(DO_mgl, digits=1), DO_pct=round(DO_pct, digits=1),
         Temp=round(Temp, digits=1), `CondmS/cm`=round(`CondmS/cm`, digits=2),
         SpCond=round(SpCond, digits=2),
         Sal=round(Sal, digits=1), pH=round(pH, digits=1))

# export df - 11/29/2018
#hl_wq_bind3 %>% 
 # write_csv("sondes/Data_output/CMP_Data_Hill_Sonde_2017_2018_Tidied.csv")
```

Step 2.

Import data from First Mallard Branch (also known as "Spring Branch") that can
be downloaded from the NERR website http://cdmo.baruch.sc.edu/ 

Note: As of November 2018, currently waiting to get Chlorophyll-a and fDOM data from Brian Bergamaschi at the USGS California Water Science Center, who also maintains a sonde
at the First Mallard site. (The NERR discontinued their collection of these at this
particular site)

## First Mallard
```{r}
# IMPORT DATA
# 2017
fm17 <- read_csv("sondes/Data/FirstMallard/FM_sonde_2017_NERRdata.csv") %>% 
  select(DateTimeStamp, cDepth, Turb, DO_mgl, DO_pct, Temp, SpCond, Sal, pH) %>% 
  mutate(cDepth=ifelse(cDepth<0, NA, cDepth)) %>%  # turn negative into NAs
  rename(datetime=DateTimeStamp, Depth=cDepth) %>% 
  mutate(Deployment=NA, `CondmS/cm`=NA) # the NERR data files don't provide this column

fm17$datetime <- mdy_hm(fm17$datetime, tz="America/Los_Angeles")

fm17_2 <- fm17 %>% 
  mutate(datetime_DLS= datetime + hours(1)) # daylight savings time adjustmt

# 2018
fm18 <- read_csv("sondes/Data/FirstMallard/FM_sonde_2018_NERRdata.csv") %>% 
  select(DateTimeStamp, cDepth, Turb, DO_mgl, DO_pct, Temp, SpCond, Sal, pH) %>% 
  mutate(cDepth=ifelse(cDepth<0, NA, cDepth)) %>%  
  rename(datetime=DateTimeStamp, Depth=cDepth) %>% 
  mutate(Deployment=NA, `CondmS/cm`=NA)

fm18$datetime <- mdy_hm(fm18$datetime, tz="America/Los_Angeles")

fm18_2 <- fm18 %>% 
  mutate(datetime_DLS= datetime + hours(1))

# final tidied df
fm_wq_bind <- rbind(fm17_2, fm18_2) %>% 
  mutate(SiteName="FM", ChlorophyllugL=NA, fDOMQSU=NA)
  # placeholders for chlorophyll and fdom until we get data from Brian Bergamaschi USGS

# export df - 11/29/2018
#fm_wq_bind %>% write_csv("sondes/Data_output/CMP_Data_FirstMallard_Sonde_2017_2018_Tidied.csv")
```

Step 3.

Create a tidy dataframe that has all sites and years

# Re-import tidy df
```{r}
# sheldrake
sheldrake <- read_csv("sondes/Data_output/CMP_Data_Sheldrake_Sonde_2017_2018_Tidied.csv")
sheldrake$datetime <- as_datetime(sheldrake$datetime, tz="America/Los_Angeles")
sheldrake$datetime_DLS <- as_datetime(sheldrake$datetime_DLS, tz="America/Los_Angeles")

# peytonia
peytonia <- read_csv("sondes/Data_output/CMP_Data_Peytonia_Sonde_2017_2018_Tidied.csv")
peytonia$datetime <- as_datetime(peytonia$datetime, tz="America/Los_Angeles")
peytonia$datetime_DLS <- as_datetime(peytonia$datetime_DLS, tz="America/Los_Angeles")

# hill
hill <- read_csv("sondes/Data_output/CMP_Data_Hill_Sonde_2017_2018_Tidied.csv") 
hill$datetime <- as_datetime(hill$datetime, tz="America/Los_Angeles")
hill$datetime_DLS <- as_datetime(hill$datetime_DLS, tz="America/Los_Angeles")

# first mallard aka spring branch
firstmallard <- read_csv("sondes/Data_output/CMP_Data_FirstMallard_Sonde_2017_2018_Tidied.csv")
firstmallard$datetime <- as_datetime(firstmallard$datetime, tz="America/Los_Angeles")
firstmallard$datetime_DLS <- as_datetime(firstmallard$datetime_DLS, tz="America/Los_Angeles")
```

Step 4. Export tidy dataframe with all sites and years (find in sonde/Data_output/.. folder)

# Export in one df
```{r}
# bind all sloughs together
wqall <- rbind(sheldrake, peytonia, hill, firstmallard) 

# create new columns
wqall$Mo <- month(wqall$datetime_DLS)
wqall$Date <- date(wqall$datetime_DLS)
wqall$Yr <- year(wqall$datetime_DLS)
wqall2 <- wqall %>% 
  mutate(Season=ifelse(Mo<6, "Spring", ifelse(Mo>8, "Autumn", "Summer"))) %>% 
  rename(Chla_field=ChlorophyllugL)  # not yet calibrated by Dahlgren lab values
  
# export df
#wqall2 %>% write_csv("sondes/Data_output/CMP_Data_Sonde_All_Sites_2017_2018_Tidied.csv")
```

Step 5. 

# Import final tidy df
```{r}
sondeall <- read_csv("sondes/Data_output/CMP_Data_Sonde_All_Sites_2017_2018_Tidied.csv")
```

